%-------------------------
% Resume in Latex
% Author : Faramarz Aboutalebi
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}

\input{glyphtounicode}

% -------------------- FONT OPTIONS --------------------
% sans-serif
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% serif
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-1in} % Default was -.5in
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Subsection formatting
\titleformat{\subsection}{
  \vspace{-4pt}\scshape\raggedright\large
}{\hspace{-.15in}}{0em}{}[\color{black}\vspace{-8pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% -------------------- CUSTOM COMMANDS --------------------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\setlength{\footskip}{4.08003pt}

% -------------------- START OF DOCUMENT --------------------
\begin{document}

% -------------------- HEADING--------------------
\begin{flushright}
  % \vspace{-4pt}
  \color{gray}
  \item
  Last Updated on January 12th, 2024
\end{flushright}

\vspace{-5pt}

\begin{center}
    \textbf{\Huge \scshape Faramarz Aboutalebi} \\ \vspace{8pt}
    \small 
    \faIcon{github}
    \href{https://github.com/FaramarzAboutalebi}{\underline{github.com/}} $  $
    \faIcon{code}
    \href{https://faramarzaboutalebi.github.io/PersonalWebsite/}
    {\underline{PersonalWebsite}} $  $
    \faIcon{linkedin}
    \href{https://www.linkedin.com/in/faramarz-aboutalebi-88335828a/}{\underline{linkedin.com/}} $  $
    \faIcon{envelope}
    \href{Fara@knights.ucf.edu}
    {\underline{Fara@knights.ucf.edu}}
\end{center}

% -------------------- EDUCATION --------------------
\section{Education}
  \resumeSubHeadingListStart

    \resumeSubheading
      {High School Math and Physics Diploma}{2015}
      

    \resumeSubheading
      {Solid State Physics Bachelor/Graduated}{July 2020}
      {Bu-Ali Sina University}{}
      
    \resumeSubheading
      {Computer Science Undergraduate}{August 2021-Current}
      {University of Central Florida }{UCF GPA: 3.561/4.0}
      
    =

    \vspace{-10pt}

    \subsection{Achievements}
      %\textbf{Courses:} Object-Oriented Programming, Data Structures \& Algorithms, Embedded Systems, Discrete Math, Linear Algebra, Calculus, Physics, Probability \& Statistics \\
      \textbf{Awards:} Benefited received a scholarship from the \textbf{Momeni Foundation} (2x), Certified Premium Deli Professional by \textbf{Boar’s Head}.

  \resumeSubHeadingListEnd

% -------------------- SKILLS --------------------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    
     \textbf{Languages}{: C/C++, Python, Java, Assembly Language, JavaScript, HTML, CSS, React, Vite, \LaTeX.} \\
     
     \textbf{Tools}{: Git/GitHub, Unix Shell, VS Code, PyCharm/IDEA, Eclipse, Android studio, Google colab, and Xcode.}
     
     % \textbf{Frameworks}{: React, Node.js, Flask, JUnit, WordPress, Material-UI, FastAPI} \\
     
     % \textbf{Libraries}{: pandas, NumPy, Matplotlib}
     
    }}
 \end{itemize}

% -------------------- PROJECTS --------------------
\section{Projects}
    \resumeSubHeadingListStart

        \resumeProjectHeading
            {\textbf{\href{https://faramarzaboutalebi.github.io/PersonalWebsite/}{\underline{Personal Website}}} $|$ \emph{\footnotesize React, JavaScript, Vite, CSS, GitHub Pages, Git, Unix Shell, VS Code}}{Jan. 2024 - Present}
        
        \resumeItemListStart
            \resumeItem{View the project on the \faIcon{github} \href{https://github.com/FaramarzAboutalebi/PersonalWebsite.git}{\underline{GitHub}}.}
            \resumeItem{Developed a personal website to showcase my portfolio and skills in web development.}
            \resumeItem{Implemented the site using React and Vite, demonstrating proficiency in modern JavaScript frameworks and build tools.}
            \resumeItem{Designed a responsive and user-friendly interface, with a focus on clean aesthetics and ease of navigation.}
            \resumeItem{Integrated a dynamic content update mechanism using React's state management and lifecycle methods.}
            \resumeItem{Successfully deployed the website using GitHub Pages, gaining practical experience in website hosting and deployment.}
            \resumeItem{Managed the project using Git, demonstrating skills in version control and collaborative development.}
        \resumeItemListEnd

        \resumeProjectHeading
            {\textbf{Software System - Compiler Project} $|$ \emph{\footnotesize C, Assembly Language, Git, Unix Shell, VS Code}}{Aug 2023 -- Nov 2023}
        
        \resumeItemListStart
            \resumeItem{Developed a comprehensive compiler for the PL/0 programming language, including a virtual machine, lexical analyzer, recursive descent parser, and advanced parser with procedural constructs:}
            \resumeItem{Implemented a P-machine to execute PL/0 assembly code, featuring a segmented process address space for instructions and data. \href{https://github.com/FaramarzAboutalebi/SoftwareSystem-CompilerProject/tree/main/HW1#readme}{\underline{ReadMe}}}
            
            \resumeItem{Created a lexical analyzer in HW2 to tokenize PL/0 source code and generate lexeme tables. \href{https://github.com/FaramarzAboutalebi/SoftwareSystem-CompilerProject/tree/main/HW2#readme}{\underline{ReadMe}}}
            \resumeItem{Developed a recursive descent parser in HW3 to analyze PL/0 program syntax, generate intermediate code, and integrate with the lexical analyzer. \href{https://github.com/FaramarzAboutalebi/SoftwareSystem-CompilerProject/tree/main/HW3#readme}{\underline{ReadMe}}}
            \resumeItem{Enhanced the parser in HW4 to support additional grammatical constructs like procedures and calls, refining syntax error detection and reporting. \href{https://github.com/FaramarzAboutalebi/SoftwareSystem-CompilerProject/tree/main/HW4#readme}{\underline{ReadMe}}}
        \resumeItemListEnd
          
    \resumeSubHeadingListEnd


% -------------------- EXPERIENCE --------------------
\section{Experience}
  \resumeSubHeadingListStart

          \resumeProjectHeading
          {\textbf{Information Technology Instructor - Intern} $|$ \footnotesize\emph{Valencia College, FL}\vspace{8pt}}{June. 2023 -- Aug. 2023}
          \resumeItemListStart
            \resumeItem{Delivered an 8-week IT program focused on JavaScript, HTML, and CSS.}
            \resumeItem{Conducted interactive classes, designed self-paced activities, and supported students in final projects.}
            \resumeItemListEnd

          \resumeProjectHeading
          {\textbf{Computer Science I undergraduate teaching assistant}\vspace{8pt} $|$ \footnotesize\emph{UCF, FL}}{Jan. 2023 -- May 2023}
          \resumeItemListStart
            \resumeItem{Responsible for conducting lab exams, teaching, and solving problems as the lab instructor.}
            \resumeItem{Grading codes, quizzes, and exams submitted by students.}
            \resumeItem{Holding office hours to respond to students' questions and help them with code debugging.}
          \resumeItemListEnd

          \resumeProjectHeading
          {\textbf{Introduction to Programming with C undergraduate teaching assistant} $|$ \footnotesize\emph{UCF, FL}\vspace{8pt}}{Aug. 2022 -- Dec.2022}
          \resumeItemListStart
            \resumeItem{Responsible for conducting lab exams, teaching, and solving problems as the lab instructor.}
            \resumeItem{Grading codes, quizzes, and exams submitted by students.}
            \resumeItem{Holding office hours to respond to students' questions and help them with code debugging.}
          \resumeItemListEnd

        
          
    \resumeSubHeadingListEnd 

\end{document}
